---
title: "Compare ISS before and after seperate boot"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidytable)
```



# What's Changed
I split the boot conditional statement into three seperate statements and coded them such that the user can turn all on or none on or any combination of the three on.


# Data



```{r}
out1 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_300iters_output_2024-08-08.RDS")

out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/separate_boot_switches_ISS_301iters_output_2024-08-13.RDS")
```




## Compare to ISS from before

```{r, fig.height=4}
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, 1.2*max(out1$iss_length$iss)), col = "black") 
lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("before split boot", "after split boot"))


```

These are a bit different. BUT, this is expected because between these changes I also fixed a mistake where strata wasn't being incorporated as intended in the saved data file from sql_downloads. So now that it is, I would expect the ISS to be a bit different. 


## Plot ISS and numnber of hauls

```{r, fig.height=4, dpi=600}
par(mfrow = c(1,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, 1.2*max(out1$iss_length$iss)), col = "black") 
lines(out1$iss_length$YEAR, out1$iss_length$nhls, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("Fishery ISS", "Number of Hauls"))

```











