---
title: "sample() vs rmultinomial()"
author: "Brett Stacy"
date: "2024-06-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(data.table)
library(tidyverse)
```

## base::sample() vs base::rmultinomial()

This document compares the functions sample() and rmultinomial() for the purposes of bootstrapping. Both these functions use a random number generator and can produce a bootstrapped sample set from either a uniform or multinomial distribution. However, sample() cannot accept a single number, where rmultinomial() can. This is relevant to observer data where there exist single sample sizes for hauls in a non-trivial number of hauls. However, rmultinomial() cannot sample without replacement, where sample() can. This is relevant to situations where alternative sampling rates are investigated. 

This document uses idealized simulated data.

Goals:

1.  Demonstrate that the following are equivalent:
    1.  sample()\*probs, sample(prob = probs), rmultinomial(prob = probs)

```{r, eval=T}


### SIDE QUEST ####
# is sampling from a multinomial with probabilities determined by frequency the same as sample()? if so, can we use the multinomial to resample considering weighitng?
# in other words, can we use the month weights to control which YAGM strata gets resampled more often?

iters = 10000
temp.lengths = c(44,45,46,46,46,47,47,48,49,50)
temp.lengthsDT = data.table(length = temp.lengths)
s.lengths = purrr::map(1:iters, ~sample(temp.lengths, replace = TRUE)) 
u.lengths = unique(temp.lengths)
n.lengths = temp.lengthsDT[, .N]
probs.lengths = tidytable::count(temp.lengthsDT, length)[,n/sum(n)] 
s.lengths2 = purrr::map(1:iters, ~sample(u.lengths, size = n.lengths, replace = TRUE, prob = probs.lengths)) 


## sample(n)
# I want to count how many times on average each number shows up in the sampled lengths
# old habits die hard, loop:
freq.list = list()
for (j in 1:length(unique(temp.lengths))) {
  freq.list[[j]] = rep(NA, iters)
  for (i in 1:iters) {
    freq.list[[j]][i] = sum(unique(temp.lengths)[j] == s.lengths[[i]])
  }
}

# lapply(freq.list, mean)


## sample(probs)
freq.list2 = list()
for (j in 1:length(unique(temp.lengths))) {
  freq.list2[[j]] = rep(NA, iters)
  for (i in 1:iters) {
    freq.list2[[j]][i] = sum(unique(temp.lengths)[j] == s.lengths2[[i]])
  }
}

# lapply(freq.list2, mean)



temp.freqDT = tidytable::count(temp.lengthsDT, length)[,setnames(.SD, "n", "true_frequency")] %>%
  mutate(true_prob = true_frequency/sum(true_frequency), sample_frequency = unlist(lapply(freq.list, mean)), sample_prob = unlist(lapply(freq.list2, mean)))
# tidytable::summarise(temp.lengthsDT, frequency = tidytable::n(), .by = length) # does the same thing as above but above is cleaner

## rmultinom(prob)
m.lengths = rmultinom(iters, temp.lengthsDT[,.N], prob = temp.freqDT$true_prob) # random multinomial based on the frequency of length l observed

temp.freqDT %>%
  mutate(rmultinom_prob = rowMeans(m.lengths)) %>%
  round(digits = 2) -> temp.freqDT

temp.freqDT
# great success! this shows that sample() is the same as rmultinomial(), one just uses frequency and the other probabilities
# this means that we can bootstrap the YAGM by weight for a particular year (YAGM/Y), then bootstrap the hauls (if any) in that YAGM, then lengths as usual.
# If there aren't any hauls in that YAGM, what happens?
### END SIDE QUEST ####


```

This demonstrates that using sample() with the vector of observations equals sample() with the probability of unique observations and using a sampling size equal to the number of observations. These are also equivalent to using rmultinom() in the same manner as the latter sample() method. 


















