---
title: "EBS Pcod Fishery ISS Assesssment Results"
author: "Brett Stacy"
output: pdf_document
header-includes:
  - \usepackage{float}
  - \floatplacement{table}{H}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "hide", dpi = 600, fig.width = 8.5, fig.pos = "H")
library(tidytable)
library(data.table)
library(reshape2)
library(ggplot2)
library(knitr)
library(stringr)
library(patchwork)
library(xtable)
library(kableExtra)
library(gt)
library(tidyr)
library(dplyr)
options(scipen = 5)
```


# Introduction
This document summarizes the impact of our bootstrap fishery composition ISS results on the 2023 EBS Pacific cod stock assessment. 




```{r}


out_1.4 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.4_ISS_1000iters_output_2025-01-23.RDS")


# save out_1.4 for Steve to plug into the assessment
out_1.4$length$iss %>% 
  select(YEAR, iss) %>% 
  write.csv(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/issb_v1_from_Brett_Stacy.csv", row.names = F)


assessment_2023_iss = tidytable(year = 1977:2023,
                                iss = c(27,
                                45,
                                54,
                                54,
                                63,
                                31,
                                117,
                                140,
                                211,
                                216,
                                396,
                                401,
                                185,
                                189,
                                1565,
                                1543,
                                913,
                                1435,
                                1561,
                                2020,
                                2142,
                                2046,
                                2722,
                                2960,
                                3140,
                                3446,
                                4301,
                                3608,
                                3455,
                                2694,
                                2115,
                                2502,
                                2218,
                                1975,
                                2596,
                                2776,
                                3293,
                                3604,
                                3324,
                                2821,
                                2469,
                                1899,
                                1367,
                                1048,
                                859,
                                1160,
                                706))




# survey vs observer length measurements
obs_numbers = tidytable(year = 1982:2023,
                        survey = c(10863,
                        13143,
                        12133,
                        17150,
                        15872,
                        9483,
                        6950,
                        4246,
                        5428,
                        7069,
                        10129,
                        10500,
                        12931,
                        9820,
                        9348,
                        9591,
                        9574,
                        11183,
                        12170,
                        19078,
                        12365,
                        11835,
                        10986,
                        11753,
                        12530,
                        13441,
                        15328,
                        23737,
                        21223,
                        25150,
                        30177,
                        19902,
                        29204,
                        19880,
                        19507,
                        15020,
                        8806,
                        23408,
                        0,
                        17397,
                        16677,
                        19943),
                        fishery = c(9658,
                                    33200,
                                    45635,
                                    66940,
                                    58257,
                                    129226,
                                    111065,
                                    58625,
                                    39698,
                                    347227,
                                    344923,
                                    248967,
                                    359147,
                                    344794,
                                    445217,
                                    474908,
                                    438746,
                                    186233,
                                    199708,
                                    210419,
                                    230802,
                                    288854,
                                    237487,
                                    228664,
                                    179782,
                                    140663,
                                    164860,
                                    147875,
                                    131514,
                                    172269,
                                    192273,
                                    211962,
                                    234476,
                                    213888,
                                    182980,
                                    157482,
                                    124004,
                                    86800,
                                    65301,
                                    55858,
                                    73025,
                                    42942))


obs_numbers %>% 
  tidytable::summarise(sum(survey), sum(fishery))


a.out = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/Derived_quants.csv")
p.out = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/parameters.csv")



```


# ISSB Results 
ISSB stands for the fishery input sample size by bootstrapping. ISSB is the time series output from our bootstrap analysis. ISSA stands for the fishery input sample size traditionally used in the assessment. 

```{r, fig.height=6}
df = data.frame(rss = out_1.4$length$rss$rss, year = as.factor(out_1.4$length$rss$YEAR))



# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(2,1), mar = c(0,3.1,0,0), oma = c(3, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000), cex.lab = 1.3) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.4$length$iss$YEAR, out_1.4$length$iss$nhls, col = "red")
legend(1977, 11000, lty = c(1,1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"), bty = "n")
text(1977, 14000, "A")



plot(out_1.4$length$iss$YEAR, out_1.4$length$iss$nss, type = "l", ylab = "Nominal Sample Size", xlab = "Year", cex.lab = 1.3) 
text(1977, 420000, "B")
mtext("Year", side = 1, line = 2, cex = 2)


# averages
out_1.4$length$iss$iss %>% mean()
assessment_2023_iss$iss %>% mean()


```







\newpage


# EBS Pcod Assessment Impact

Steve B. ran the published 2023 stock assessment version with ISSB to see if it impacted the assessment outcomes. The below results are from stock assessment runs with Francis tuning, although Steve also produced runs without tuning. 



## Tables of parameters

These tables include the point estimates and standard deviations (SD) of selected parameters and quantities with the original 2023 assessment configuration using ISSA and the modified using ISSB. Both the untuned and tuned results are shown. The values highlighted in grey are the only values exceeding an absolute percent difference of 10\%

\newpage

### Tuned

```{r, results="hide"}
p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)"),
                    MODEL2%in%c("OM tuned", "Fiss tuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM tuned", "Fiss tuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table

p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)", "L_at_Amin_Fem_GP_1", "Richards_Fem_GP_1", "LnQ_base_Survey(2)", "Size_DblN_peak_Fishery(1)", "Size_DblN_ascend_se_Fishery(1)",
                               "Size_DblN_peak_Survey(2)", "Size_DblN_ascend_se_Survey(2)"),
                    MODEL2%in%c("OM tuned", "Fiss tuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM tuned", "Fiss tuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table.full




# possible solution:
# cols_order <- unlist(lapply(c("a", "b", "c"), function(x) paste(x, c("Count", "Percent"), sep = "_")))
cols_order <- unlist(lapply(c("Value", "StdDev"), function(x) paste(x, c("OM tuned", "Fiss tuned"), sep = "_")))

data_wide <- p.table %>% 
        pivot_wider(names_from = "MODEL2", values_from = c(Value, StdDev), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))

# percent difference?
data_wide %>% 
  tidytable::mutate(diff.val = 100*abs(`Value_OM tuned` - `Value_Fiss tuned`)/`Value_OM tuned`,
                    diff.sd = 100*abs(`StdDev_OM tuned` - `StdDev_Fiss tuned`)/`StdDev_OM tuned`)



data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(4, 5),
             decimals = 0) %>% 
  fmt_number(rows = c(1,3),
             columns = c(2),
             decimals = 2)
```




```{r, results="hide"}
p.table %>% 
  tidytable::rename("Point Estimate" = Value, "SD" = StdDev) %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM tuned", "ISSA tuned", "ISSB tuned")) -> p.table2
  
cols_order <- unlist(lapply(c("Point Estimate", "SD"), function(x) paste(x, c("ISSA tuned", "ISSB tuned"), sep = "_")))

data_wide <- p.table2 %>% 
        pivot_wider(names_from = "MODEL2", values_from = c("Point Estimate", "SD"), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))



data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(4, 5),
             decimals = 0) %>% 
  fmt_number(rows = c(1,3),
             columns = c(2),
             decimals = 2) %>% 
  fmt_number(rows = c(1,3),
             columns = c(3),
             decimals = 2) %>% 
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(5),
      rows = c(5, 7, 9)))

```




```{r, results="show"}
p.table.full %>% 
  tidytable::rename("Point Estimate" = Value, "SD" = StdDev) %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM tuned", "ISSA tuned", "ISSB tuned")) -> p.table2
  
cols_order <- unlist(lapply(c("Point Estimate", "SD"), function(x) paste(x, c("ISSA tuned", "ISSB tuned"), sep = "_")))

data_wide <- p.table2 %>% 
        pivot_wider(names_from = "MODEL2", values_from = c("Point Estimate", "SD"), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))



# # percent difference?
# data_wide %>% 
#   tidytable::mutate(diff.val = 100*abs((`Point Estimate_ISSA tuned` - `Point Estimate_ISSB tuned`)/`Point Estimate_ISSA tuned`),
#                     diff.sd = 100*abs((`SD_ISSA tuned` - `SD_ISSB tuned`)/`SD_ISSA tuned`)) 




data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(11, 12),
             decimals = 0) %>% 
  fmt_number(rows = c(1,2,5,7,9),
             columns = c(2,3),
             decimals = 2) %>% 
  # tab_style(style = list(cell_fill("grey")),
  #           locations = cells_body(
  #     columns = c(5),
  #     rows = c(5, 7, 9)))
    tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(2,3),
      rows = c(6))) %>% 
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(4,5),
      rows = c(8,12,14,16))) -> tuned.table
tuned.table


```

<!-- \begin{table}[H] -->
<!-- \centering -->
<!-- ```{r, results='asis', echo=FALSE} -->
<!-- gt::as_latex(tuned.table) %>%  -->
<!--   cat(sep = "") -->

<!-- ``` -->
<!-- \end{table} -->



\newpage


### Tuned with added params

\newpage

```{r, results="hide"}


p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)", "L_at_Amin_Fem_GP_1", "Richards_Fem_GP_1", "LnQ_base_Survey(2)", "Size_DblN_peak_Fishery(1)", "Size_DblN_ascend_se_Fishery(1)",
                               "Size_DblN_peak_Survey(2)", "Size_DblN_ascend_se_Survey(2)", "Size_DblN_peak_Fishery(1)_BLK4repl_1977", "Size_DblN_ascend_se_Fishery(1)_BLK4repl_1977"),
                    MODEL2%in%c("OM tuned", "Fiss tuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM tuned", "Fiss tuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table.full



```



\blandscape

```{r, results="show"}
p.table.full %>% 
  tidytable::rename("Point Estimate" = Value, "SD" = StdDev) %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM tuned", "ISSA tuned", "ISSB tuned")) -> p.table2
  
cols_order <- unlist(lapply(c("Point Estimate", "SD"), function(x) paste(x, c("ISSA tuned", "ISSB tuned"), sep = "_")))

data_wide <- p.table2 %>% 
        pivot_wider(names_from = "MODEL2", values_from = c("Point Estimate", "SD"), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))



# # percent difference?
# data_wide %>%
#   tidytable::mutate(diff.val = 100*abs((`Point Estimate_ISSA tuned` - `Point Estimate_ISSB tuned`)/`Point Estimate_ISSA tuned`),
#                     diff.sd = 100*abs((`SD_ISSA tuned` - `SD_ISSB tuned`)/`SD_ISSA tuned`))


data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(11, 12)+2,
             decimals = 0) %>% 
  fmt_number(rows = c(1,2,5,7,9),
             columns = c(2,3),
             decimals = 2) %>% 
  # tab_style(style = list(cell_fill("grey")),
  #           locations = cells_body(
  #     columns = c(5),
  #     rows = c(5, 7, 9)))
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(2,3),
      rows = c(6))) %>% 
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(4,5),
      rows = c(8,11,12,14,16,18))) -> tuned.table
tuned.table


```


\elandscape








\newpage

### Untuned

```{r, results="hide"}

p.out %>% 
  tidytable::filter(Label%in%c("VonBert_K_Fem_GP_1", "L_at_Amax_Fem_GP_1", "SR_LN(R0)", "L_at_Amin_Fem_GP_1", "Richards_Fem_GP_1", "LnQ_base_Survey(2)", "Size_DblN_peak_Fishery(1)", "Size_DblN_ascend_se_Fishery(1)",
                               "Size_DblN_peak_Survey(2)", "Size_DblN_ascend_se_Survey(2)"),
                    MODEL2%in%c("OM untuned", "Fiss untuned")) %>% 
  tidytable::mutate(StdDev = Parm_StDev) %>% 
  tidytable::select(-Parm_StDev) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(Label%in%c("SSB_2023", "SSB_2038", "Bratio_2023", "Bratio_2038", "SPRratio_2023", "SPRratio_2038"),
                                           MODEL2%in%c("OM untuned", "Fiss untuned"))) %>% 
  tidytable::select(-X, -MODEL, -HI, -LO) -> p.table.full



```





```{r, results="show"}
p.table.full %>% 
  tidytable::rename("Point Estimate" = Value, "SD" = StdDev) %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM untuned", "ISSA untuned", "ISSB untuned")) -> p.table2
  
cols_order <- unlist(lapply(c("Point Estimate", "SD"), function(x) paste(x, c("ISSA untuned", "ISSB untuned"), sep = "_")))

data_wide <- p.table2 %>% 
        pivot_wider(names_from = "MODEL2", values_from = c("Point Estimate", "SD"), names_glue = "{.value}_{MODEL2}") %>% 
        # Reorder columns
        select(all_of(c("Label", cols_order)))



# # percent difference?
# data_wide %>% 
#   tidytable::mutate(diff.val = 100*abs((`Point Estimate_ISSA untuned` - `Point Estimate_ISSB untuned`)/`Point Estimate_ISSA untuned`),
#                     diff.sd = 100*abs((`SD_ISSA untuned` - `SD_ISSB untuned`)/`SD_ISSA untuned`)) 
# 
# 


data_wide %>% 
        gt(rowname_col = "Label") %>%
        tab_spanner_delim(delim = "_") %>% 
  fmt_number(decimals = 4) %>% 
  fmt_number(rows = c(11, 12),
             decimals = 0) %>% 
  fmt_number(rows = c(1,2,5,7,9),
             columns = c(2,3),
             decimals = 2) %>% 
  # tab_style(style = list(cell_fill("grey")),
  #           locations = cells_body(
  #     columns = c(5),
  #     rows = c(5, 7, 9)))
    tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(2,3),
      rows = c(6))) %>% 
  tab_style(style = list(cell_fill("grey")),
            locations = cells_body(
      columns = c(4,5),
      rows = c(7,14)))

```



\newpage


### Plots old

```{r}

a.out %>% glimpse()

SSB.names = paste0("SSB_", 1977:2038)
SPRratio.names = paste0("SPRratio_", 1977:2038)
Bratio.names = paste0("Bratio_", 1977:2038)


SSB = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%SSB.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%SSB.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 5, 8)))
SPRratio = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%SPRratio.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%SPRratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 10, 13)))
Bratio = a.out %>% 
  tidytable::filter(MODEL2 == "OM tuned", Label%in%Bratio.names) %>% 
  tidytable::bind_rows(a.out %>% 
                         tidytable::filter(MODEL2 == "Fiss tuned", Label%in%Bratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11)))




SSB %>% 
  tidytable::rename(Model_run = MODEL2) %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_run, linetype = Model_run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("SSB") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))



SPRratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = MODEL2, linetype = MODEL2)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("SPRratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.3), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black")
Bratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = MODEL2, linetype = MODEL2)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Bratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black")
```



<!-- # Scratch: percent differences of all params -->
<!-- ```{r} -->

<!-- p.out = tidytable(p.out) -->

<!-- p.out %>%  -->
<!--   filter(MODEL2=="OM tuned") %>%  -->
<!--   pull(Value) -> temp1 -->
<!-- p.out %>%  -->
<!--   filter(MODEL2=="Fiss tuned") %>%  -->
<!--   pull(Value) -> temp2 -->
<!-- p.out %>%  -->
<!--   filter(MODEL2=="OM tuned") %>%  -->
<!--   pull(Parm_StDev) -> temp1.2 -->
<!-- p.out %>%  -->
<!--   filter(MODEL2=="Fiss tuned") %>%  -->
<!--   pull(Parm_StDev) -> temp2.2 -->
<!-- p.error = tidytable(value = 100*abs((temp1-temp2)/temp1), -->
<!--                     SD = 100*abs((temp1.2-temp2.2)/temp1.2)) -->

<!-- barplot(p.error$value) -->

<!-- ``` -->





### Plots 

\newpage

```{r, fig.height=10}
a.out %>% glimpse()

SSB.names = paste0("SSB_", 1977:2038)
SPRratio.names = paste0("SPRratio_", 1977:2038)
Bratio.names = paste0("Bratio_", 1977:2038)
rec.names = paste0("Recr_", 1977:2038)

a.out %>% 
  tidytable::mutate(MODEL2 = ifelse(MODEL2 == "OM tuned",
                                    "ISSA tuned",
                                    ifelse(MODEL2 == "OM untuned", 
                                           "ISSA untuned",
                                           ifelse(MODEL2 == "Fiss tuned", "ISSB tuned", "ISSB untuned")))) %>% 
  tidytable::rename(Model_Run = MODEL2) -> a.out.2

# tuned

SSB = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA tuned", Label%in%SSB.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%SSB.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 5, 8)))

SPRratio = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA tuned", Label%in%SPRratio.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%SPRratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 10, 13)))

Bratio = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA tuned", Label%in%Bratio.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%Bratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11)))


Recruitment = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA tuned", Label%in%rec.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB tuned", Label%in%rec.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 6, 9)))



p1 = SSB %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("") + 
  ylab("SSB") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  geom_text(aes(x=2023, label="Assessment Year 2023", y=750000), colour="blue", angle=90, vjust = 1.2) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p2 = SPRratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("") + 
  ylab("SPRratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.3), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p3 = Bratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Bratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  geom_hline(yintercept = .35, linetype = "dashed", color = "black") +
  geom_text(aes(x=1985, label="Management Target = 0.35", y=.38), colour="blue", angle=0) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))




p1 + plot_spacer() + p2 + plot_spacer() + p3 + plot_layout(ncol = 1,
                           heights = c(6, -.5, 6, -.5, 6))
```

\newpage

```{r, fig.height=4}
p4 = Recruitment %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Recruitment") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
p4

```


\newpage

```{r, fig.height=10}
# untuned

SSB = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA untuned", Label%in%SSB.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB untuned", Label%in%SSB.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 5, 8)))

SPRratio = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA untuned", Label%in%SPRratio.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB untuned", Label%in%SPRratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 10, 13)))

Bratio = a.out.2 %>% 
  tidytable::filter(Model_Run == "ISSA untuned", Label%in%Bratio.names) %>% 
  tidytable::bind_rows(a.out.2 %>% 
                         tidytable::filter(Model_Run == "ISSB untuned", Label%in%Bratio.names)) %>% 
  tidytable::mutate(Year = as.numeric(substr(Label, 8, 11)))




p1 = SSB %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("") + 
  ylab("SSB") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  geom_text(aes(x=2023, label="Assessment Year 2023", y=750000), colour="blue", angle=90, vjust = 1.2) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p2 = SPRratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("") + 
  ylab("SPRratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.3), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))

p3 = Bratio %>% 
  ggplot(aes(x = Year, y = Value, ymin = LO, ymax = HI, fill = Model_Run, linetype = Model_Run)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  xlab("Year") + 
  ylab("Bratio") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.85), 
        legend.direction = "vertical", 
        legend.box = "vertical") +
  geom_vline(xintercept = 2023, linetype = "dashed", color = "black") +
  geom_hline(yintercept = .35, linetype = "dashed", color = "black") +
  geom_text(aes(x=1985, label="Management Target = 0.35", y=.38), colour="blue", angle=0) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))



p1 + plot_spacer() + p2 + plot_spacer() + p3 + plot_layout(ncol = 1,
                           heights = c(6, -.5, 6, -.5, 6))


```


\newpage

# M

```{r, fig.height=8}
profiles = read.csv("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/Fishery ISS Paper/from Steve B/Likelihoods_by_fleet.csv")



profiles %>%
  tidytable::filter(Label=="Length_like", variable=="Fishery") %>% 
  mutate(Model_Run = ifelse(MODEL=="Model_23.1.0.d_NEW_FISS_tuned", "ISSB", "ISSA")) -> profiles.2


profiles.2 %>% 
  ggplot(aes(x = M, y = Diff, group = Model_Run, color = Model_Run)) +
  geom_line() +
  geom_point() +
  geom_vline(xintercept = 0.3866, linetype = "dashed", color = "black") +
  geom_text(aes(x = 0.38, label = "Fixed M=0.3866", y = 1.5), colour="blue", angle=90, vjust = 1.2) +
  geom_hline(yintercept = 0) +
  labs(x = "M", y = "Change in -LL for Fishery Length Comps") +
  theme_classic() +
  theme(legend.position = c(.8, .8))








```





